\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}

% Source of this custom command: tex.stackexchange.com/a/294990
\usepackage{tikz}
\newcommand{\ExternalLink}{
  \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{
    \begin{scope}[x=1ex, y=1ex]
      \clip (-0.1,-0.1) 
      --++ (-0, 1.2) 
      --++ (0.6, 0) 
      --++ (0, -0.6) 
      --++ (0.6, 0) 
      --++ (0, -1);
      \path[draw, 
        line width = 0.5, 
        rounded corners=0.5] 
      (0,0) rectangle (1,1);
    \end{scope}
    \path[draw, line width = 0.5] (0.5, 0.5) 
    -- (1, 1);
    \path[draw, line width = 0.5] (0.6, 1) 
    -- (1, 1) -- (1, 0.6);
  }
}

\newcommand{\CVAuthor}{Philippe Olivier}
\newcommand{\CVWebpage}{github.com/PhilippeOlivier}

\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=false,
bookmarksopen=false,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}
\pagenumbering{gobble}

\usepackage{comment}
% % for english
\includecomment{english}
% \excludecomment{french}
%  for french
%\includecomment{french}
%\excludecomment{english}

\begin{document}

%%%%%%%%%
% TITRE %
%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{mailto:philippe.olivier@polymtl.ca}
{Philippe.Olivier@polymtl.ca}
\,\SubBulletSymbol\,
514.433.5700
\,\SubBulletSymbol\,
\href{https://www.github.com/PhilippeOlivier}
{\url{\CVWebpage}\ExternalLink}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%
  
    \Section
    {Education}{}{}

    \Entry
    \textbf{Polytechnique Montréal}

    PhD, Computer Engineering
    \hfill
    Aug. 2016 -- May 2021

    \Gap
    \BulletItem
    Thesis: Fairness in Combinatorial Optimization

    \Gap
    \BulletItem
    Research supervisors: Gilles Pesant and Andrea Lodi

    \BigGap
    \Entry
    \textbf{Université Laval}

    B.S., Computer Science
    \hfill
    Aug. 2012 -- May 2016
  
%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}{}{}

\Entry
\textbf{Research Interests}

\Gap
\BulletItem
Operations research
\Gap
\BulletItem
Combinatorial optimization
\Gap
\BulletItem
Constraint programming
\Gap
\BulletItem
Integer programming

\BigGap
\Entry
\textbf{Publications}

\Gap\Gap
\href{https://arxiv.org/abs/2101.03716}
{Lodi, A., Olivier, P., Pesant, G., and Sankaranarayanan S. (2022) "Fairness over Time in Dynamic Resource Allocation with an Application in Healthcare". \emph{Mathematical Programming}.}\ExternalLink}

\Gap\Gap
\href{https://doi.org/10.1007/s10288-021-00486-x}
{Olivier, P., Lodi, A., and Pesant, G. (2021) "Measures of Balance in Combinatorial Optimization". \emph{4OR}.}\ExternalLink}

\Gap\Gap
\href{https://doi.org/10.1287/ijoc.2020.0983}
{Olivier, P., Lodi, A., and Pesant, G. (2020) "The Quadratic Multiknapsack Problem with Conflicts and Balance Constraints". \emph{INFORMS Journal on Computing}.}\ExternalLink}

\Gap\Gap
\href{https://doi.org/10.1007/978-3-319-93031-2_33}
{Olivier, P., Lodi, A., and Pesant, G. (2018) "A Comparison of Optimization Methods for Multi-Objective Constrained Bin Packing Problems". In \emph{Integration of AI and OR Techniques in Constraint Programming, Delft, Netherlands, (CPAIOR 2018)}.\ExternalLink}

\BigGap
\Entry
\textbf{Conference Presentations}

\Gap\Gap
CPAIOR 2018 (Delft, Netherlands)
\hfill
June 2018
\begin{Detail}\href{http://icaps18.icaps-conference.org/schedule}{A Comparison of Optimization Methods for Multi-Objective Constrained Bin Packing Problems\ExternalLink}\end{Detail}

\Gap\Gap
JOPT 2018 (Montreal, Canada)
\hfill
May 2018
\begin{Detail}\href{https://symposia.gerad.ca/jopt2018/en/schedule?slot_id=1374}{A Comparison of Optimization Methods for Multi-Objective Constrained Bin Packing Problems\ExternalLink}\end{Detail}

\Gap\Gap
IFORS 2017 (Quebec, Canada)
\hfill
July 2017
\begin{Detail}\href{https://www.euro-online.org/conf/ifors2017/treat_abstract?paperid=1523}{Solving the Wedding Seating Problem by Constraint Programming\ExternalLink}\end{Detail}

\BigGap
\Entry
\textbf{Poster Presentations}

\Gap\Gap
CP 2019 (Stamford, United States)
\hfill
Oct. 2019
\begin{Detail}Measures of Balance in Combinatorial Optimization\end{Detail}

\BigGap
\Entry
\textbf{Member}

\Gap\Gap
\href{https://www.polymtl.ca/labo-quosseca/en/members/alumni/doctoral-students}
{Laboratoire Quosséça\ExternalLink}
\hfill
Aug. 2016 -- May 2021

\Gap\Gap
\href{http://cerc-datascience.polymtl.ca/person/philippe-olivier}
{Canada Excellence Research Chair in Data Science for Real-Time Decision-Making\ExternalLink}
\hfill
Aug. 2016 -- May 2021

%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEACHING EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Teaching Experience}{}{}

\Entry
\textbf{Université du Québec à Montréal}

Course Lecturer
\BulletItem
INF1070: Administration of Computer Systems
\hfill
Jan. 2022 -- May 2022
\small \\ Commands, applications, and management of a Linux system. \normalsize

\Gap\Gap
\Entry
\textbf{Polytechnique Montréal}

Course Lecturer
\BulletItem
INF1005D: Procedural Programming in Python
\hfill
Sept. 2021 -- Dec. 2021
\small \\ Introduction to Python programming. \normalsize

\Gap\Gap
Teaching Assistant
\BulletItem
INF4705/INF8775: Algorithm Design
\hfill
Jan. 2018 -- Dec. 2019
\small \\ Asymptotic notation, complexity classes, algorithm design patterns, metaheuristics. \normalsize

\pagebreak % temp

\Gap\Gap
\Entry
\textbf{Université Laval}

\Gap\Gap
Teaching Assistant
\hfill Sept. 2013 -- Dec. 2013

%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%

\Section
{Work \quad\quad Experience}{}{}

\Entry
\textbf{Hydro-Québec TransÉnergie}

Intern
\hfill
Sept. 2014 -- Apr. 2015
\small \\ Automating the data transfer between a database and specialized software. Automating some of the tests done by electrical engineers.\normalsize

%%%%%%%%%%%%%
%% PROJCETS %%
%%%%%%%%%%%%%

\Section
{Projects}{}{}

\Entry
\textbf{Fantasy Solver}

DFS Solver
\hfill
June 2021 -- Now
\small \\ Solver for optimal lineup generation in multi-entry \emph{Daily Fantasy Sports} (DFS) tourneys. It is, to my knowledge, the only exact solver for generating a provably optimal set of lineups for DFS tourneys.\normalsize

%%%%%%%%%%%%%%%%%%%
%% CONTRIBUTIONS %%
%%%%%%%%%%%%%%%%%%%

%% \Section
%% {Contributions}{}{}

%% \Entry
%% \textbf{CSPLib: A problem library for constraints}

%% Problem XXX: The Wedding Seating Problem
%% \hfill
%% DATE

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% COMPÉTENCES TECHNIQUES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap\Gap % Temporary, to ensure page break
% \Section
% {Compétences techniques}{}{}

% \Entry
% \textbf{Langages}

% Python, C++, Bash

% \Gap\Gap
% \Entry
% \textbf{Outils}

% CPLEX, CP Optimizer (ILOG), Gurobi, SCIP, MiniZinc, Git, Linux, \LaTeX

\end{Body}

\end{document}


%\Gap\Gap
% \href{https://www.ift.ulaval.ca/vie-etudiante/prix-pierre-ardouin/}{Prix Pierre Ardouin\ExternalLink}
% \hfill Winter 2014
% \small \\ Best project in software engineering. \normalsize
